Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-17 main.tex
:pencil: Update literature review

	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes and considered \gls{sic} from primary to backscatter link.
	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver.
	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we propose the concept of Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

@@

\end{section}

\begin{section}{Backscatter Principles}
	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\\
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\\
		\subfloat[Scatter Model]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}

	% \begin{figure*}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.3\linewidth}{!}{
	% 			\input{assets/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.35\linewidth}{!}{
	% 			\input{assets/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.27\linewidth}{!}{
	% 			\input{assets/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure*}

	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

	\begin{subsection}{Backscatter Modulation}
		In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
		As such, there exists a mapping from the alphabet to the set.
		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.

		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.

@@

>>>>

	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
	The former is impratical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

@@

	\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
	$j$ represents the imaginary unit.
	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
	% $\boldsymbol{I}$ represents the identity matrix.
	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1} \mid \sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
	% $\odot$ denotes the Hadamard product.
	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
	$\sim$ means ``distributed as''.
	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
\end{section}

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\\
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.95\columnwidth}{!}{
	% 			\input{assets/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\\
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure}

	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure*}

	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the node absorbs a portion of the impinging wave and scatters the remaining to the space.
	The absorbed signal can be used for information decoding and energy harvesting \cite{Kim2021a}, while the scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	Related to structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch, and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
	% The scatter model is illustrated in Fig. \subref*{fi:scatter_model}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ candidate states, and the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

	\begin{subsection}{Backscatter Modulation}
		% In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
		% To perform backscatter modulation, nodes encode message within distribution of reflection states.%
		% To perform backscatter modulation, nodes encode message within distribution of reflection states.%
		Backscatter nodes encode message by frequently change its reflection state.

		% Although most backscatter and \gls{sr} literatures assumed equiprobable state distribution at nodes, the

		within distribution of reflection states and

		% In backscatter modulation, the tag \emph{periodically varies} the reflection coefficient to embed its own information.
		% As such, there exists a mapping from the alphabet to the set.
		For $M$-ary \gls{qam}, the complex constellation point $c_m$ maps to the corresponding reflection coefficient by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $\alpha \in [0,1]$ models the amplitude scatter ratio at the direction of interest.

@@

		When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
